\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{booktabs}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage{longtable}
\linespread{0.95} % Reduce overall line spacing
\setlength{\parskip}{0.5em} % Reduce vertical space between paragraphs
\setlength{\parindent}{0pt}

\begin{document}

% --- Cover Letter ---
Prof. Andrew J. Steinmetz\\
Department of Physics, The University of Arizona\\
Email: ajsteinmetz@arizona.edu\\
Phone: (520) 989-1305\\

April 5, 2025

\vspace{1em}

\noindent
Visiting Assistant Professor of Physics Search Committee\\
The Department of Physics and Astronomy, University of Tampa\\
Tampa, FL

\vspace{1em}

\noindent
Dear Members of the Search Committee,

\vspace{1em}

I am writing to apply for the Visiting Assistant Professor of Physics at the University of Tampa. I have a PhD in Physics from the University of Arizona (UA), and a research background in theoretical relativistic spin dynamics, magnetism, and cosmology. I have extensive experience teaching physics at the undergraduate level as well as managing laboratory courses, therefore, I believe I am an excellent candidate for this position.

My current role is that of Global Professor at UA with a joint appointment in the Arizona College of Technology (ACT), Hebei University of Technology (HEBUT) in Tianjin, China. Prior to my current position at the UA, I was an adjunct faculty member at Pima where I was the instructor-of-record for introductory astronomy and physics courses managing both the lecture and laboratory components of the courses. After being hired as a Global Professor at UA, I went on to teach intermediate to upper division physics courses (i.e. theoretical mechanics, quantum mechanics). I'm active in student mentoring as well as the organizer for the physics journal club at ACT.

At ACT/HEBUT, I successfully designed and implemented a two-semester advanced undergraduate physics laboratory curriculum, coordinating closely with laboratory managers, equipment vendors, and contractors (communicating mostly in Chinese via a translator) to refurbish a laboratory room and acquire equipment under tight deadlines. I am proud to say we now have a fully functional multipurpose undergraduate laboratory for our ACT students. I also co-developed the Senior Design/Capstone course that emphasized career skills and group work in an engineering context. Our first graduates of the program will earn their degrees this June. Given all of these skills I've developed in my career so far, I am excited to bring my expertise to UTampa.

In addition to my teaching qualifications, I have continued to advance my research profile with regular publications in cosmology, strong field physics, and statistical mechanics. Two recent publications are Steinmetz \& Rafelski ``Short Note on Spin Magnetization in QGP'' \emph{Eur Phys J ST} (in press, 2025) and Birrell et al. ``Fermi-Dirac Integrals in Degenerate Regimes: Novel Asymptotic Expansion'' \emph{Int J Theor Phys} (2024). The first work outlines a theory of cosmic magnetism in the early universe based on quark-gluon plasma magnetization while the second explores novel expansions of the Fermi-Dirac distribution for degenerate gases. I look forward to continuing my research at UTampa as well as collaboration with faculty.

As a resident of South Tampa, the Visiting Assistant Professor position is even more attractive as I would be able to remain home year-round. While I haven't yet visited the UTampa campus, I have passed by it several times on the Tampa river walk and found the campus beautiful from across the river.

Thank you for your consideration and I look forward to hearing back from the committee.

\vspace{1em}

\noindent
Sincerely,

\vspace{2em}

\noindent
Prof. Andrew J. Steinmetz\\
Global Professor, Department of Physics\\
The University of Arizona

\end{document}
