\documentclass[11pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{booktabs}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage{longtable}
\linespread{0.95} % Reduce overall line spacing
\setlength{\parskip}{0.5em} % Reduce vertical space between paragraphs
\setlength{\parindent}{0pt}

\usepackage{hyperxmp}
\hypersetup{
  pdftitle   = {Steinmetz CV 2025-06},
  pdfauthor  = {Andrew J. Steinmetz},
  pdfsubject = {Curriculum Vitae},
  pdfkeywords = {
    Physics, Spin Dynamics, Magnetism, Neutrinos, Relativistic Quantum Mechanics, Quark-Gluon Plasma, Curriculum Vitae, Andrew Steinmetz
  },
  pdfproducer = {LaTeX with pdfTeX},
  pdfcreator  = {Andrew J. Steinmetz},
%  pdfcreationdate = {D:20250619090000Z},
  colorlinks = true,
  urlcolor   = blue,
  linkcolor  = blue
}

\begin{document}

\begin{center}
    {\Large\textbf{Andrew James Steinmetz, Ph.D.}}\\[0.5em]
    {\large Curriculum Vitae -- Last Updated June 2025}
\end{center}

{\normalsize
\begin{center}
    \begin{tabular}{@{}p{2.0cm} p{5.0cm} p{2.0cm} p{5.0cm}@{}}
        \textbf{Email:} & \href{mailto:ajsteinmetz@arizona.edu}{ajsteinmetz@arizona.edu} &
        \textbf{Website:} & \href{https://ajsteinmetz.github.io/}{https://ajsteinmetz.github.io/} \\
        \textbf{Phone:} & (520) 989-1305 &
        \textbf{ORCID:} & \href{https://orcid.org/0000-0001-5474-2649}{0000-0001-5474-2649} \\
    \end{tabular}
\end{center}
}

\medskip

{\Large\textbf{Employment}}

{\normalsize
\begin{tabular}{@{}p{3.8cm} p{4.4cm} p{5.3cm} p{3.0cm}@{}}
    \toprule
    \textbf{Position Title} & \textbf{Department} & \textbf{Institution} & \textbf{Dates} \\
    \midrule
    Academic Professional & School of Physics & Georgia Institute of Technology & {\footnotesize Jan.~2025 (expected)} \\ 
    Global Professor\textbf{*} & Arizona College of Tech. & Hebei University of Technology & {\footnotesize Feb.~2024--June 2025} \\
    Global Professor\textbf{*} & Dept. of Physics & The University of Arizona              & {\footnotesize Nov.~2023--June 2025} \\
    Adjunct Faculty  & Physics/Astronomy Dept. & Pima Community College       & {\footnotesize June~2020--Dec.~2023} \\
    \bottomrule
\end{tabular}
}

\textbf{*} Joint international faculty appointment.

\medskip

{\Large\textbf{Education}}

{\normalsize
\begin{tabular}{@{}p{2.8cm} p{5.0cm} p{5.5cm} p{3.2cm}@{}}
    \toprule
    \textbf{Degree} & \textbf{Field} & \textbf{Institution} & \textbf{Dates} \\
    \midrule
    Ph.D. & Physics             & The University of Arizona & Dec. 2023 \\
    B.S.   & Physics             & The University of Arizona & May 2014 \\
    B.S.   & Chemical Engineering& The University of Arizona & May 2014 \\
    \bottomrule
\end{tabular}
}

\medskip

{\Large\textbf{Research Interests}}

\begin{itemize}[leftmargin=*,nosep]
    \item \textbf{Relativistic Spin Dynamics:} Exploring non-minimal (and nonlinear) electromagnetism (EM) in quantum mechanics utilizing the Klein-Gordon-Pauli (KGP) equation, or classically via modifying the covariant Thomas-Bargman-Michel-Telegdi (TMBT) torque equation.
    \item \textbf{Neutrino Physics:} EM mixing of neutrino flavor through transition magnetic dipole moments as a possible probe of the hierarchy problem. Exploring possible EM-induced neutrino mass splitting.
    \item \textbf{Cosmic Magnetization:} Magnetized spin-polarized thermal plasmas during the electron-positron and quark-gluon-plasma (QGP) epochs as a possible origin of primordial magnetic fields (PMF).
\end{itemize}

\medskip

{\Large\textbf{Dissertation}}

\textbf{Title:} Modern Topics in Relativistic Spin Dynamics and Magnetism\\[0.3em]
\textbf{Committee:} Dr. Johann Rafelski~(Chair), Dr. Shufang Su~(Member), Dr. John Rutherfoord~(Member), Dr. Stefan Meinel~(Member), Dr. Sean Fleming~(Member)\\[0.3em]
\textbf{HDL:} \href{http://hdl.handle.net/10150/670301}{http://hdl.handle.net/10150/670301} \textbf{Presentation:} \href{http://dx.doi.org/10.13140/RG.2.2.24323.27689}{10.13140/RG.2.2.24323.27689}

\noindent\rule{\linewidth}{1.0pt}

{\Large\textbf{Publications}}

Citations = 125; h-index = 7 (\href{https://scholar.google.com/citations?user=fJBK1GIAAAAJ}{Google Scholar}, June 2025). See also \href{https://inspirehep.net/authors/1796313}{INSPIRE-HEP} and \href{https://arxiv.org/a/steinmetz_a_1.html}{arXiv}.

{\large\textbf{Peer-Reviewed Journal Articles}}

\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{\href{https://github.com/ajsteinmetz/short-note-qgp}{Steinmetz, A.}}, Rafelski, J. ``Short note on spin magnetization in QGP,'' \textit{Eur. Phys. J. Spec. Top.} (2025), \href{https://doi.org/10.1140/epjs/s11734-025-01625-9}{10.1140/epjs/s11734-025-01625-9}.
    \item Birrell, J., Formanek, M., \textbf{\href{https://github.com/ajsteinmetz/fermi-distribution}{Steinmetz, A.}}, Yang, C. T., Rafelski, J. ``Fermi-Dirac Integrals in Degenerate Regimes: Novel Asymptotic Expansion,'' \textit{Int. J. Theor. Phys.} 63, 163 (2024),\\ \href{https://doi.org/10.1007/s10773-024-05695-8}{10.1007/s10773-024-05695-8}.
    \item Rafelski, J., \textbf{\href{https://github.com/ajsteinmetz/neutrino-transition-moments}{Steinmetz, A.}}, Yang, C. T. ``Dynamic fermion flavor mixing through transition dipole moments,'' \textit{Int. J. Mod. Phys. A} 38.31 (2023): 2350163, \href{https://doi.org/10.1142/S0217751X23501634}{10.1142/S0217751X23501634}.
    \item \textbf{\href{https://github.com/ajsteinmetz/plasma-partition}{Steinmetz, A.}}, Yang, C. T., Rafelski, J. ``Matter-antimatter origin of cosmic magnetism,'' \textit{Phys. Rev. D} 108 (2023): 123522, \href{https://doi.org/10.1103/PhysRevD.108.123522}{10.1103/PhysRevD.108.123522}.
    \item Formanek, M., \textbf{Steinmetz, A.}, Rafelski, J. ``Motion of classical charged particles with magnetic moment in external plane-wave electromagnetic fields,'' \textit{Phys. Rev. A} 103.5 (2021): 052218, \href{https://doi.org/10.1103/PhysRevA.103.052218}{10.1103/PhysRevA.103.052218}.
    \item Formanek, M., \textbf{Steinmetz, A.}, Rafelski, J. ``Radiation reaction friction: Resistive material medium,'' \textit{Phys. Rev. D} 102.5 (2020): 056015, \href{https://doi.org/10.1103/PhysRevD.102.056015}{10.1103/PhysRevD.102.056015}.
    \item Formanek, M., \textbf{Steinmetz, A.}, Rafelski, J. ``Classical neutral point particle in linearly polarized EM plane wave field,'' \textit{Plasma Phys. Control. Fusion} 61.8 (2019): 084006, \href{https://doi.org/10.1088/1361-6587/ab242e}{10.1088/1361-6587/ab242e}.
    \item \textbf{\href{https://github.com/ajsteinmetz/magnetic-dipole-moment}{Steinmetz, A.}}, Formanek, M., Rafelski, J. ``Magnetic dipole moment in relativistic quantum mechanics,'' \textit{Eur. Phys. J. A} 55, 40 (2019), \href{https://doi.org/10.1140/epja/i2019-12715-5}{10.1140/epja/i2019-12715-5}.
    \item Formanek, M., Evans, S., Rafelski, J., \textbf{Steinmetz, A.}, Yang, C. T. ``Strong fields and neutral particle magnetic moment dynamics,'' \textit{Plasma Phys. Control. Fusion} 60.7 (2018), \href{https://doi.org/10.1088/1361-6587/aac06a}{10.1088/1361-6587/aac06a}.
    \item Rafelski, J., Formanek, M., \textbf{Steinmetz, A.} ``Relativistic dynamics of point magnetic moment'' \textit{Eur. Phys. J. C} 78 (2018): 1--12, \href{https://doi.org/10.1140/epjc/s10052-017-5493-2}{10.1140/epjc/s10052-017-5493-2}.
\end{enumerate}

\medskip

{\large\textbf{Book Chapters \& Review Articles}}

\begin{enumerate}[leftmargin=*,nosep]
    \item Rafelski, J., Birrell, J., Grayson, C., \textbf{\href{https://github.com/ajsteinmetz/thesis-collab-project}{Steinmetz, A.}}, Yang, C. T. ``Quarks to Cosmos: Particles and Plasma in Cosmological evolution,'' \textit{Eur. Phys. J. Spec. Top.} (2025), \href{https://doi.org/10.1140/epjs/s11734-025-01470-w}{10.1140/epjs/s11734-025-01470-w}.
    \item Rafelski, J., \textbf{Steinmetz, A.}, Yang, C. T. ``Dynamic Flavor Mixing Through Transition Moments,'' \textit{Harald Fritzsch Memorial Volume}, pp. 269--284 (2024), \href{https://doi.org/10.1142/9789811292279_0015}{10.1142/9789811292279\_0015}.
    \item Rafelski, J., Birrell, J., \textbf{\href{https://github.com/ajsteinmetz/a-short-survey}{Steinmetz, A.}}, Yang, C.T. ``A Short Survey of Matter-Antimatter Evolution in the Primordial Universe,'' \textit{Universe} 9.7 (2023): 309, \href{https://doi.org/10.3390/universe9070309}{10.3390/universe9070309}.
\end{enumerate}

\medskip

{\large\textbf{Works in Progress}}

\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{Steinmetz, A.}, Evans, S., Formanek, M., Grayson, C., Labun, L., Price, W., Rafelski, J. ``Strong fields in classical and quantum physics,'' (in preparation, 2025).
    \item \textbf{Steinmetz, A.}, Rafelski, J. ``Magnetized primordial heavy-quark plasma,'' (in preparation, 2025).
    \item \textbf{Steinmetz, A.}, Yang, C. T., Rafelski, J. ``Electromagnetic field forcing of dynamic CP-violation in lepton sector,'' (in preparation, 2025).
    \item Evans, S., \textbf{Steinmetz, A.} ``Anomalous magnetic moment in the QCD vacuum,'' (in preparation, 2025).
\end{enumerate}

\medskip

{\Large\textbf{Conference Presentations \& Talks}}

{\large\textbf{Talks Presented by Steinmetz, A.}}

\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{Steinmetz, A.}, Yang, C.~T., Rafelski, J. ``Primordial Cosmic Magnetism.'' \textit{SMT 30th Anniversary Steward Observatory Symposium}, The University of Arizona, Tucson, Arizona, September 22, 2023. \href{http://dx.doi.org/10.13140/RG.2.2.19213.24806}{10.13140/RG.2.2.19213.24806}.
    \item \textbf{Steinmetz, A.}, Yang, C.~T., Rafelski, J. ``Magnetism in the Cosmic Plasma Epoch.'' \textit{ELI-Beamlines Strong Fields Frontiers}, The Extreme Light Infrastructure ERIC, Prague, Czech Republic, June 13, 2023. \href{http://dx.doi.org/10.13140/RG.2.2.32635.02087}{10.13140/RG.2.2.32635.02087}.
    \item \textbf{Steinmetz, A.}, Yang, C.~T., Rafelski, J. ``Magnetism in the Cosmic Plasma Epoch.'' \textit{Margaret Island Symposium on Particles and Plasmas (PP2023)}, HUN-REN Wigner Research Centre for Physics, Budapest, Hungary, June 8, 2023. \href{http://dx.doi.org/10.13140/RG.2.2.29279.57762}{10.13140/RG.2.2.29279.57762}.
    \item \textbf{Steinmetz, A.} ``Relativistic Two-Body Quantum Mechanics.'' The University of Arizona, Tucson, Arizona, March 2017.
\end{enumerate}

{\large\textbf{Talks Co-Prepared by Steinmetz, A. (Presented by Others)}}

\begin{enumerate}[leftmargin=*,nosep]
    %\item Rafelski, J. (presenter), Yang, C. T., \textbf{Steinmetz, A.} ``Non-Stationary Quark-gluon Plasma in the Universe'' \textit{Hungarian-German WE-Heraeus Seminar}, Goerlitz \& HZDR Dresden, Germany, June, 2025.
    \item Rafelski, J. (presenter), Yang, C. T., \textbf{Steinmetz, A.} ``Thermal Non-equilibrium and Quark-gluon Plasma'' \textit{Joint European Thermodynamics Conference (JETC 2025)}, Belgrade, Serbia, May 28, 2025. \href{http://dx.doi.org/10.13140/RG.2.2.25443.05922}{10.13140/RG.2.2.25443.05922}
    \item Rafelski, J. (presenter), Birrell, J., Grayson, C., \textbf{Steinmetz, A.}, Yang, C.~T., Foster, S. ``Quarks to Cosmos: Particles and Plasma in Cosmological Evolution.'' \textit{16th Conference on Quark Confinement and the Hadron Spectrum (QCHSC 2024)}, The University of Adelaide, Cairns, Australia, August 9, 2024.\\ \href{http://dx.doi.org/10.13140/RG.2.2.19642.30407}{10.13140/RG.2.2.19642.30407}.
    \item Rafelski, J. (presenter), Yang, C.~T., Birrell, J., Grayson, C., Foster, S., \textbf{Steinmetz, A.} ``Particles \& Plasmas in the First Hour of the Universe.'' \textit{Particles \& Plasmas Symposium (PP2024)}, HUN-REN Wigner Research Centre for Physics, Budapest, Hungary, June 11, 2024. \href{http://dx.doi.org/10.13140/RG.2.2.22997.74727}{10.13140/RG.2.2.22997.74727}.
    \item Rafelski, J. (presenter), \textbf{Steinmetz, A.} ``Space-time, Acceleration and Matter.'' The Extreme Light Infrastructure ERIC, Prague, Czech Republic, December 2022. \href{http://dx.doi.org/10.13140/RG.2.2.25933.76001}{10.13140/RG.2.2.25933.76001}.
    \item Rafelski, J. (presenter), Yang, C.~T., Birrell, J., Grayson, C., \textbf{Steinmetz, A.} ``Particles and Plasmas in the Universe.'' \textit{22nd Zimanyi School Winter Workshop on Heavy Ion Physics}, HUN-REN Wigner Research Centre for Physics, Budapest, Hungary, December 2022. \href{http://dx.doi.org/10.13140/RG.2.2.27611.48160}{10.13140/RG.2.2.27611.48160}.
    \item Rafelski, J. (presenter), \textbf{Steinmetz, A.} ``Strong Field Physics: Report on Frankfurt School and Current Arizona Effort.'' \textit{Margaret Island Symposium on Particles \& Plasmas (PP2022)}, HUN-REN Wigner Research Centre for Physics, Budapest, Hungary, May 17, 2022. \href{http://dx.doi.org/10.13140/RG.2.2.13363.13600}{10.13140/RG.2.2.13363.13600}
\end{enumerate}

\noindent In addition, I have closely collaborated on preparing research and academic talks delivered at the following conferences/institutes: Deutsche Elektronen-Synchrotron/DESY (2024), Margaret Island Symposium on Particles \& Plasmas (PP2023), Polish Academy of Science at Warsaw University (2023), XI International Conference on New Frontiers in Physics (ICNFP 2022), The University of Arizona (2022), Hungarian Academy of Sciences (2022), Institute of Theoretical Physics Uniwersytet Wroclawski (2022), 21st Zimanyi School Winter Workshop on Heavy Ion Physics (2021), 4th LeCosPA Symposium (2021).

\medskip

{\Large\textbf{Grants \& Awards}}

\begin{itemize}[leftmargin=*,nosep]
    \item 2023 Young Researcher Meeting Grant, European Physical Journal (EPJ), Springer-Verlag (PP2023)
    \item 2023 Fanfare Graduate Travel Award, The University of Arizona (PP2023, ELI-Beamlines)
\end{itemize}

\medskip

{\Large\textbf{Teaching Experience}}

\textbf{Key:} UA (The University of Arizona), ACT (Arizona College of Tech.), PCC (Pima Community College)

\textbf{Faculty Courses at UA/ACT (as Instructor-of-Record)*:}\\
{\normalsize
\begin{tabular}{@{}p{2.5cm} p{6.0cm} p{2.0cm} p{2.0cm} p{3.0cm}@{}}
    \toprule
    \textbf{Course \#} & \textbf{Title} & \textbf{Sections} & \textbf{Students} & \textbf{Semester} \\
    \midrule
    PHYS 371   & Quantum Theory                    & 1 & 75  & Spring 2025 \\
    PHYS 381   & Methods in Exp. Physics I         & 2 & 67  & Spring 2025 \\
    PHYS 321   & Theoretical Mechanics             & 2 & 139 & Fall 2024 \\
    PHYS 382   & Methods in Exp. Physics II\textbf{**}       & 2 & 46  & Fall 2024 \\
    ENGR 498A  & Senior Design/Capstone\textbf{**}           & 1 & 43  & Fall 2024 \\
    PHYS 240   & Intro. Electricity \& Magnetism    & 3 & 203 & Spring 2024 \\
    PHYS 381   & Methods in Exp. Physics I\textbf{**}        & 2 & 50  & Spring 2024 \\
    \bottomrule
\end{tabular}
}\\[0.0em]

\textbf{*} Full teaching record and recent student course evaluations available upon request.\\[0.0em]
\textbf{**} First time offered at this institution. Designed, developed, and delivered curriculum.

\begin{itemize}[leftmargin=*,nosep]
    \item \textbf{Adjunct Courses at PCC (Physics \& Astronomy Dept., as Instructor-of-Record):} Intro. Physics I/II (2020, 2021, 2023), The Solar System (2020--2023), Intro. Electricity \& Magnetism (2022)
    \item \textbf{TA Courses at UA (Dept. of Physics, Dept. of Chemistry \& Biochemistry):} Intro. to Scientific Computing (2017), Intro. Electricity \& Magnetism (2017), Methods in Exp. Physics I/II (2018, 2019), Intro. Mechanics I/II Lab (2020), Intro. Physics I/II Lab (2020), General Chemistry I(Honors)/II Lab (2019, 2021--2023)
\end{itemize}

\medskip

{\Large\textbf{Curriculum Development \& Institutional Reports}}
\begin{itemize}[leftmargin=*,nosep]
    \item \textbf{Steinmetz, A.} \textit{Status and Outlook of PHYS 381/382 -- Methods in Experimental Physics I/II at ACT/HEBUT.} Internal report submitted to the University of Arizona Department of Physics, June 2025. Proposed curricular adjustments and \$36,000 USD laboratory equipment expansion in response to enrollment growth and infrastructure constraints at ACT/HEBUT.
    \item \textbf{Steinmetz, A.} ``Physics Lab, Journal Club, and AI Tools.'' Presentation, \textit{Cross College Faculty Forum (CCFF).} Arizona College of Technology, Hebei University of Technology. April 11, 2025.
    \item Advanced Physics Laboratory (PHYS 381/382), ACT/HEBUT. Developed full-year experimental physics lab curriculum, advising and guidance for the purchasing of +\$14,000 USD (+\textyen 100,000 RMB) in new equipment, and coordinated instruction for 100+ undergraduate students (2024--2025).
    \item Senior Design/Capstone (ENGR 498A), ACT/HEBUT. Co-developed a one-semester senior design and career preparation curriculum, and coordinated instruction for 40+ undergraduate students (2024).
\end{itemize}

\medskip

{\Large\textbf{Academic Service \& Associations}}

\begin{itemize}[leftmargin=*,nosep]
    \item Associate Designated Campus Colleague (DCC), Department of Physics, The University of Arizona, (2025--present).
    \item Organizer, Undergraduate Journal Club, Hebei University of Technology, (2025).
    \item Member, Cross College Faculty Forum (CCFF), Arizona College of Technology, Hebei University of Technology (2024--2025)
    \item Member, Department of Physics, University of Arizona, Faculty Search Committee(s), (2024, 2025).
    \item Reviewer for \textit{Physical Review D}, \textit{Physical Review Research}, \textit{European Physics Journal Plus}, \textit{Modern Physics Letters A}, \textit{International Journal of Modern Physics A}, and \textit{ICPMS 2025}.
    \item Member, American Physical Society (APS).
\end{itemize}

\medskip

{\large\textbf{Public Outreach}}

\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{Steinmetz, A.} (2024, November 7). Proving that SU(2) is compact (and other group theory bits) \href{https://ajsteinmetz.github.io/mathematics/2024/11/07/su2-compactness.html}{Link}
    \item \textbf{Steinmetz, A.} (2024, October 17). Einstein’s mass-energy and kinetic energy. \href{https://ajsteinmetz.github.io/physics/2024/10/17/kinetic-energy-coefficient.html}{Link}
    \item \textbf{Steinmetz, A.} (2024, October 16). Can we ever detect the graviton? \href{https://ajsteinmetz.github.io/physics/2024/10/16/graviton-detector.html}{Link}
\end{enumerate}

\medskip

{\Large\textbf{External \& Institutional Press}}

\begin{enumerate}[leftmargin=*,nosep]
  \item World Scientific Publishing. (2025, January 9). ``The International Journal of Modern Physics A (IJMPA) Celebrates 40 Years of Excellence,'' \textit{LinkedIn}. \href{https://www.linkedin.com/posts/world-scientific-publishing_the-international-journal-of-modern-physics-activity-7282999555967610880-SJ78}{Link}.
  \item Hebei University of Technology. (2024, November 20). ``Cross-College Faculty Forum between Arizona Tech and Hebei University of Technology successfully held'' [translated]. \textit{Hebei University of Technology News}. \href{https://hatech.hebut.edu.cn/xw/62ff3dcc665b453898ec92841d45e0ce.htm}{Link}.
  \item Kong, X. (2024, March 20). ``Professor Andrew Steinmetz of the University of Arizona Visited the Physics Demonstration and Exploration Laboratory'' [translated]. \textit{Physics Experiments at HEBUT, Hebei University of Technology}. \href{https://mp.weixin.qq.com/s?__biz=Mzg4Njg3NjQyMw==&mid=2247484302&idx=1&sn=273f88bc0332d9a34a9fdbee01b196b3&chksm=cf93b3e6f8e43af0b75b832801bbe9e684d258f00c3671e7e625bfccde7c74a387ef9e5a9926&mpshare=1&scene=24&srcid=0320Wt3iZMGOxbLpRBZg9nYA}{Link}.
  \item The University of Arizona, Department of Physics. (2024, January 26). ``Announcing Department of Physics new Faculty Member Prof.\ Andrew Steinmetz,'' \textit{UA Science Physics}. \href{https://w3.physics.arizona.edu/news/announcing-department-physics-new-faculty-member-prof-andrew-steinmetz}{Link}.
  \item The University of Arizona, Department of Physics. (2023, July 25). ``International Symposium on ‘Particles and Plasmas’ and ‘Strong Fields’,'' \textit{UA Science Physics}. \href{https://w3.physics.arizona.edu/news/international-symposium-particles-and-plasmas-and-strong-fields}{Link}.
  \item Springer. (2018, January 29). ``Relativity matters: Two opposing views of the magnetic force reconciled,'' \textit{Phys.org}. \href{https://phys.org/news/2018-01-relativity-opposing-views-magnetic.html}{Phys.org}, \href{https://www.epj.org/epjc-news/1422-epjc-highlight-relativity-matters-two-opposing-views-of-the-magnetic-force-reconciled}{EPJ C Highlight}, \href{https://www.springer.com/gp/about-springer/media/research-news/all-english-research-news/relativity-matters--two-opposing-views-of-the-magnetic-force-reconciled/15417658}{Springer Press}, \href{https://www.sciencedaily.com/releases/2018/01/180129131327.htm}{ScienceDaily}; also featured in EuroPhysicsNews, EurekAlert!, Science Newsline, Sky Nightly, Space Daily.
\end{enumerate}

\medskip

{\Large\textbf{Other Links and Websites}}

\medskip

\begin{tabular}{@{}p{0.45\textwidth} p{0.45\textwidth}@{}}
  \textbf{Professional} & \textbf{Socials} \\[0.0em]
  \begin{itemize}[leftmargin=*,nosep]
    \item \href{https://w3.physics.arizona.edu/person/andrew-steinmetz}{UA Faculty Page}
    \item \href{https://github.com/ajsteinmetz}{GitHub}
    \item \href{https://www.linkedin.com/in/ajsteinmetz/}{LinkedIn}
  \end{itemize}
&
  \begin{itemize}[leftmargin=*,nosep]
    \item \href{https://bsky.app/profile/ajsteinmetz.com}{BlueSky}
    \item \href{https://www.astrobin.com/users/djinn/}{AstroBin}
    \item \href{https://en.wikipedia.org/wiki/User:CosmologicalDefect}{Wikipedia Userpage}
  \end{itemize}
\end{tabular}

My Erd\H{o}s number is 5. \href{https://mathscinet.ams.org/mathscinet/freetools/collab-dist?source=1443426&target=189017}{(Source)}

%\medskip
\newpage

{\Large\textbf{Professional References}}

{\normalsize
\begin{enumerate}[leftmargin=*,nosep]
    \item \textbf{Dr. Johann Rafelski} -- Professor of Physics, University of Arizona.\\
    Email: \href{mailto:johannr@arizona.edu}{johannr@arizona.edu} \quad Phone: (520) 777-9519
    \item \textbf{Dr. Shufang Su} -- Department Head, Professor of Physics, University of Arizona\\
    Email: \href{mailto:shufang@arizona.edu}{shufang@arizona.edu} \quad Phone: (520) 621-5540
    \item \textbf{Dr. Srin Manne} -- Associate Professor of Physics, University of Arizona\\
    Email: \href{mailto:smanne@physics.arizona.edu}{smanne@physics.arizona.edu} \quad Phone: (520) 626-5305
    \item \textbf{Dr. Ajith Rajapaksha} -- Global Professor, University of Arizona\\
    Email: \href{mailto:ajithr@arizona.edu}{ajithr@arizona.edu}
    \item \textbf{Dr. Martin Formanek} -- Marie Sklodowska-Curie Fellow, ELI-Beamlines ERIC\\
    Email: \href{mailto:martin.formanek@eli-beams.eu}{martin.formanek@eli-beams.eu} \quad Phone: (520) 248-6053
    \item \textbf{Dr. Sagar Samtani} -- Associate Professor, Director of DSAIL, Indiana University\\
    Email: \href{mailto:ssamtani@iu.edu}{ssamtani@iu.edu} \quad Phone: (812) 855-8925
\end{enumerate}
}

\end{document}
