\documentclass[11pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{booktabs}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[shortlabels]{enumitem}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{subcaption}
\linespread{0.95} % Reduce overall line spacing
\setlength{\parskip}{0.05em} % Small parskip
%\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    {\large\textbf{Status of Research Projects}}
\end{center}

\begin{itemize}[leftmargin=1.5em,nosep]
    \item \emph{Magnetized Primordial Quark-Gluon Plasma:} (first author, in preparation, 2025) A follow-up to \href{https://doi.org/10.48550/arXiv.2502.05052}{Steinmetz \& Rafelski, (2025)} investigating the role of magnetic fields during the QGP epoch with further theoretical and numerical developments of early-universe magnetization processes around hadronization. \\
    \textbf{Current status:} 
    \begin{enumerate}
        \item Partial manuscript complete. Needs to be reworked in light of already published material.
        \item Numerical implementation of calculations required to obtain concrete results.
        \item Implement theory of mass corrections.
        \item Implement theory of heavy-particle species which are non-relativistic and thus more easily magnetized. 
        \item Implement discussion of free-energy reduction.
        \item \textbf{Idea:} Evaluation of the induced cosmic electrical fields (and currents) as the cosmic spin magnetic fields are depleted. Spin to Ampere fields. Separate paper?
    \end{enumerate} 
    \item \emph{Electromagnetic Field Forcing of Dynamic CP-Violation in the Lepton Sector:} (first author, in preparation, 2025) Addressing how strong EM fields can induce dynamic CP-violation in the lepton sector, with potential implications for physics beyond the Standard Model.\\ 
    \textbf{Current status:}
    \begin{enumerate}
        \item Partial manuscript complete.
        \item Finish polishing of toy-model
        \item Implement 3-flavor calculations in a more realistic model (or at least discuss features of such a model).
        \item Implement 3-flavor calculations for EM-flavor rotation as followup to \href{https://doi.org/10.1142/S0217751X23501634}{Rafelski el al., (2023)}. Seperate paper?
    \end{enumerate}
\end{itemize}



\end{document}
